%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Implementation of Consensus} % Job title
    {Project} % Role
    {Role: Researcher} % Location
    {Aug. 2023 -} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implement PBFT consensus}
        \item {Research and Develop FALCON consensus}
        \item {Develop sharding on distributed network with PBFT}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Development of Blockchain Unified Wallet} % Job title
    {Blockchain Project} % Role
    {Role: Server Developer} % Location
    {Jan. 2022 -} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Develop the digital currency wallet which supports with various blockchain network}
        \item {Build Ethereum Client managing system on server and Apply to application}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Development of P2P-based joint ordering web service} % Job title
    {Ethereum Project} % Role
    {Role: Development Leader} % Location
    {Sep. 2021 - Oct. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Ethereum with Metamask, without DB and Backend Server}
        \item {Learn Smart Contract weakness and complement to Decentralization}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Development of University Student's Subject Management Chatbot Service} % Job title
    {Project} % Role
    {Role: Developer} % Location
    {Mar. 2021 - Jun. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development Automated System for scraping student subject information using python}
        \item {Knowledge for Network and threads using programming}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Development of process time series data clustering algorithm using deep learning} % Job title
    {AI Project} % Role
    {Role: Team Leader} % Location
    {Sep. 2020 - Jun. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {CNN, Autoencoder}
        \item {Design and Train CNN model for labeling data}
        \item {Learn how to model neural network and clustering algorithms}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Development of stock price prediction and automated trading system using AI} % Job title
    {AI Project} % Role
    {Role: Team Leader} % Location
    {Sep. 2020 - Dec. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {LSTM, Reinforcement Learning}
        \item {Implement automated trading system with Reinforcement Learning}
        \item {Learn How Deep Learning and Reinforcement Learning works}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Development of a mobile app that provides an easy and transparent donation platform} % Job title
    {Project} % Role
    {Role: iOS Developer} % Location
    {Jun. 6th 2019 - Jul. 13th 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Develop iOS mobile application for the service}
        \item {Learn Mobile App Lifecycle and how to build up mobile application}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Development of a mobile app that provides support business matching service for startups} % Job title
    {Project} % Role
    {Role: iOS Developer} % Location
    {Dec. 23th 2018 - Jan. 12th 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Support for development iOS mobile Application}
        \item {Design iOS mobile UI with storyboard}
      \end{cvitems}
    }

%---------------------------------------------------------
%   \cventry
%     {Freelance Penetration Tester} % Job title
%     {SAMSUNG Electronics} % Organization
%     {S.Korea} % Location
%     {Sep. 2013, Mar. 2011 - Oct. 2011} % Date(s)
%     {
%       \begin{cvsubentries}
%         \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
%         \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
%       \end{cvsubentries}
%     }

%---------------------------------------------------------
\end{cventries}
