%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Course Student} % Affiliation/role
    {Blockchain System Engineer Training Course} % Course Name
    {Subjected By IITP} % Location / Organization
    {May. 2021 - Nov. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Learn for Blockchain business basic theory, Web development, Ethereum Smart Contract, Hyperledger}
        \item {A program that learns core blockchain tech through practical projects}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Course Student} % Affiliation/role
    {Public Blockchain Introductory Course} % Organization/group
    {Subjected By NIPA} % Location
    {Jun. 29th 2020 - Jul. 3rd 2020 (40hr)} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Learn what public blockchain is and how to work}
        \item {Help for understanding bitcoin, ethereum basic technology }
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Course Student} % Affiliation/role
    {2019 Likelion 7th Course} % Course Name
    {Subjected By Likelion} % Location / Organization
    {Jan. 2019 - Dec. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Education for Web Programming to simply build web service using Django}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Attendance} % Affiliation/role
    {Tech Forum by Ground X 2019} % Course Name
    {Subjected By Ground X} % Location / Organization
    {Nov. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Introduction Klaytn Network and its consensus algorithm, also blockchain services based on Klaytn}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Course Student} % Affiliation/role
    {Univ. Students IT Venture Alliance, SOPT 24th iOS Department} % Course Name
    {Subjected By SOPT} % Location / Organization
    {Mar. 2019 - Jul. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Education for how to build iOS mobile application}
        \item {Proceed practical mobile app project for 2weeks}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Attendance} % Affiliation/role
    {2019 Blockchain Pyeongchang Forum (BPF)} % Course Name
    {Subjected By Gangwon Province} % Location / Organization
    {Jan. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Introduce various Blockchain Services and Platforms}
        \item {Lectures about future of blockchain from 2019}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Course Student} % Affiliation/role
    {Univ. Students IT Venture Alliance, SOPT 23rd iOS Department} % Course Name
    {Subjected By SOPT} % Location / Organization
    {Jul. 2018 - Jan. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Education for how to build iOS mobile application}
        \item {Proceed practical mobile app project for 2weeks}
      \end{cvitems}
    }
    
%---------------------------------------------------------
\end{cventries}
